---
title: "Joining Review Exercises"
author: "Your Name Here"
date: "`r format(Sys.time(), '%B %d, %Y')`"
format:
  html:
    self-contained: true
    toc: true
    toc-location: left
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)

```


# Load the datasets

```{r}

counties_demographics <- readRDS(here("data", "counties_demographics.rds"))
counties_elexresults <- readRDS(here("data", "counties_elexresults.rds"))
counties_rural_urban_suburban <- readRDS(here("data", "counties_rural_urban_suburban.rds"))



```

# Exercises

Join together the election results and urban/suburban/rural tables above, and then use the merged table to:

-   filter for just Virginia

-   group/summarize to calculate the mean pct of Trump 2020 vote by urban/rural categories

```{r}
county_info_combined <- left_join(counties_elexresults, counties_rural_urban_suburban)



```

```{r}
county_info_combined %>% 
  filter(state_code == "VA") %>% 
  group_by(rural_urban) %>% 
  summarise(mean_vote = mean(pct_r_2020))
  




```

Now using the joined dataset, come up with two groupings you find interesting or newsworthy in a particular state, and replicate the steps above them them instead.

(i.e. instead of for urban/rural, perhaps you want to look at pct of white college grads in Michigan, etc. If you're having trouble, you can stick with Virginia as your state.)

```{r}
county_info_combined %>% 
  group_by(rural_urban, winner_2020) %>% 
  summarize(count = n())
```


```{r}
county_info_combined %>% 
  group_by(rural_urban) %>% 
  summarize(sd_dem = sd(pct_d_2020),
            sd_rep = sd(pct_r_2020))
```
